PANNEURO_analysis

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
Fixed error with ESS frequencies.

@@

```{r ESS raw score frequencies}
ess_frequencies <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.col.names)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sum_score_raw) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

```{r ess clinical categories}
dat.raw <- dat.raw %>% 
  mutate(ess.cutoff.scores =
           case_when(ess.col.names <= 10 ~ "Normal sleepiness",
                     ess.col.names > 10 & ess.col.names <= 14 ~ "Mild sleepiness",
                     ess.col.names > 14 & ess.col.names <= 17 ~ "Moderate sleepiness",
                     ess.col.names > 17 & ess.col.names <= 24 ~ "Severe sleepiness",
                     )
           )

@@

```{r ESS clinical categories frequencies}
ess_frequencies <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.cutoff.scores)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.cutoff.scores) %>%
  mutate(Prop = round(n/sum(n), 2))

```{r nmsw col names, include = FALSE}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names

>>>>

```{r bmi recode}

@@

```{r ESS raw scores by Covid case}
ess_frequencies <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sum_score_raw)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sum_score_raw) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

```{r ess clinical categories}
dat.raw <- dat.raw %>% 
  mutate(ess.cutoff.scores =
           case_when(ess.sum_score_raw <= 10 ~ "Normal sleepiness",
                     ess.sum_score_raw > 10 & ess.sum_score_raw <= 14 ~ "Mild sleepiness",
                     ess.sum_score_raw > 14 & ess.sum_score_raw <= 17 ~ "Moderate sleepiness",
                     ess.sum_score_raw > 17 & ess.sum_score_raw <= 24 ~ "Severe sleepiness",
                     )
           )

@@

```{r ESS clinical categories frequencies}
ess_frequencies_clinical <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sum_score_raw)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.cutoff.scores) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(ess_frequencies_clinical)
```

# NMSW
```{r nmsw col names, include = FALSE}
nmsw.col.names <- dat.raw %>%
  select(
    starts_with("nmsw") & ends_with("numeric")
  ) %>% 
  colnames()
nmsw.col.names
